What Can Stack Traces Tell us about the Use of Exceptions in Java?

### 2014-05-09 android-stacks.tex
new conclusion

>>>>

In this work, we mined and analyzed the stack traces embedded in all issues 
of Java projects available GitHub focusing our attention on the stack traces reported on
a subset of 482 Android projects. In this study the exception information available 
on stack traces was used in combination with source code and bytecode analysis to 
pin-point patterns of exceptions (mis-)use in Java. In this study some patterns of exception
(mis)-use were consistently detected such as: unexpected wrappings (e.g., Errors
being wrapped in checked exceptions), revealing that Java hybrid exception
model is not fully used according to its purpose; undocumented runtime
exceptions signaled by third party code (which makes almost impossible for
library clients to protect against such exceptions); and a high prevalence of
java.lang exceptions reported on issues (representing approximately 50\% of the
analyzed issues). Such (mis)uses detected in out study can negatively affecting the 
robustness of current Java software systems.  As a result, there is a need for both 
improving the design of exception handling code in Java 
and developing tools support to help developers dealing with such problems.
